Efficient toolkit implementing best practices for principal component analysis of population genetic data

### 2020-05-04 paper-bedpca-supp.tex
reformat & submit

%% LyX 1.3 created this file.  For more info, see http://www.lyx.org/.
%% Do not edit unless you really know what you are doing.
\documentclass[english, 12pt]{article}
\usepackage{times}
%\usepackage{algorithm2e}
\usepackage{url}
\usepackage{bbm}
\usepackage[T1]{fontenc}
\usepackage[latin1]{inputenc}
\usepackage{geometry}
\geometry{verbose,letterpaper,tmargin=2cm,bmargin=2cm,lmargin=1.5cm,rmargin=1.5cm}
\usepackage{rotating}
\usepackage{color}
\usepackage{graphicx}
\usepackage{subcaption}
\usepackage{amsmath, amsthm, amssymb}
\usepackage{setspace}
\usepackage{lineno}
\usepackage{hyperref}
\usepackage{bbm}
\usepackage{makecell}

@@

@@

\section*{Supplementary Materials}

@@

@@

\begin{figure}[htbp]
\centering
\begin{subfigure}[b]{0.55\textwidth}
\includegraphics[width=\textwidth]{hist-outliers2-1000G.pdf}
\caption{Distribution of statistics (S2) and default threshold (6, in red)}
\end{subfigure}
\\~\\
\begin{subfigure}[b]{0.45\textwidth}
\includegraphics[width=\textwidth]{outliers2-1000G.pdf}
\caption{Principal Component (PC) scores 13 to 20 of 1000G, colored by statistic used to detect outliers (maximum number of SDs from the mean, log-scale).}
\end{subfigure}
~~~~~~
\begin{subfigure}[b]{0.45\textwidth}
\includegraphics[width=\textwidth]{be-outlier2-1000G.pdf}
\caption{Principal Component (PC) scores 13 to 20 of 1000G, colored by being detected as an outlier.\\}
\end{subfigure}
\caption{Outlier detection in the 1000 Genomes (1000G) project, using the rule ``6 SDs from the mean'', i.e.\ where S2 is the maximum (for all PCs) number of SDs from the mean (Section \ref{outlier-sample}).\label{fig:outlier-sd}}
\end{figure}

@@

\begin{figure}[htbp]
\centering
\begin{subfigure}[b]{0.45\textwidth}
\includegraphics[width=\textwidth]{UKBB-White-British.png}
\caption{PCs 1 to 20 of UKBB, colored by whether it is in the group of ``White British'' reported by the UKBB (blue).}
\end{subfigure}
~~~~~~
\begin{subfigure}[b]{0.5\textwidth}
\includegraphics[width=\textwidth]{UKBB-Maha-dist.png}
\caption{PCs 1 to 20 of UKBB, colored by robust Mahalanobis distances computed on PCs (log-scale).\\}
\end{subfigure}
\\~\\
\begin{subfigure}[b]{0.45\textwidth}
\includegraphics[width=\textwidth]{hist-Maha-dist.pdf}
\caption{Distribution of (log squared) distances.\\~\\~\\~\\~\\}
\end{subfigure}
~~~~~~
\begin{subfigure}[b]{0.45\textwidth}
\includegraphics[width=\textwidth]{UKBB-Maha-outlier.png}
\caption{PCs 1 to 20 of UKBB, colored by being detected as an outlier. Threshold of being considered as an outlier is determined based on histogram (c), where the threshold of 5 is chosen for the logarithm of the distances.}
\end{subfigure}
\caption{Homogeneous sample detection in the UK Biobank (UKBB), using robust Mahalanobis distances computed on the first 20 Principal Component scores (PCs) of UKBB.).\label{fig:homogeneous}}
\end{figure}

>>>>

%% LyX 1.3 created this file.  For more info, see http://www.lyx.org/.
%% Do not edit unless you really know what you are doing.
\documentclass[english, 12pt]{article}
\usepackage{times}
%\usepackage{algorithm2e}
\usepackage{url}
\usepackage{bbm}
\usepackage[T1]{fontenc}
\usepackage[latin1]{inputenc}
\usepackage{geometry}
\geometry{verbose,letterpaper,tmargin=2cm,bmargin=2cm,lmargin=1.5cm,rmargin=1.5cm}
\usepackage{rotating}
\usepackage{color}
\usepackage{graphicx}
\usepackage{amsmath, amsthm, amssymb}
\usepackage{setspace}
\usepackage{lineno}
\usepackage{hyperref}
\usepackage{bbm}
\usepackage{makecell}

@@

\usepackage{float}
\usepackage[caption = false]{subfig}

@@

%\section*{Supplementary Materials}

@@

\bibliographystyle{natbib}
\bibliography{refs.bib}

@@

\begin{figure}[htbp]
	\centering
	\subfloat[Distribution of statistics (S2) and default threshold (6, in red)]{\includegraphics[width=0.55\textwidth]{hist-outliers2-1000G.pdf}} \\~\\
	\subfloat[Principal Component (PC) scores 13 to 20 of 1000G, colored by statistic used to detect outliers (maximum number of SDs from the mean, log-scale).]{\includegraphics[width=0.45\textwidth]{outliers2-1000G.pdf}} $~~~~~~$
	\subfloat[Principal Component (PC) scores 13 to 20 of 1000G, colored by being detected as an outlier.\\]{\includegraphics[width=0.45\textwidth]{be-outlier2-1000G.pdf}}
	\caption{Outlier detection in the 1000 Genomes (1000G) project, using the rule ``6 SDs from the mean'', i.e.\ where S2 is the maximum (for all PCs) number of SDs from the mean (Section 2.4).\label{fig:outlier-sd}}
\end{figure}

@@

\begin{figure}[htbp]
	\centering
	\subfloat[PCs 1 to 20 of UKBB, colored by whether it is in the group of ``White British'' reported by the UKBB (blue).]{\includegraphics[width=0.45\textwidth]{UKBB-White-British.png}} $~~~~~~$
	\subfloat[PCs 1 to 20 of UKBB, colored by robust Mahalanobis distances computed on PCs (log-scale).\\]{\includegraphics[width=0.45\textwidth]{UKBB-Maha-dist.png}} \\~\\
	\subfloat[Distribution of (log squared) distances.\\~\\~\\~\\~\\).]{\includegraphics[width=0.45\textwidth]{hist-Maha-dist.pdf}} $~~~~~~$
	\subfloat[PCs 1 to 20 of UKBB, colored by being detected as an outlier. Threshold of being considered as an outlier is determined based on histogram (c), where the threshold of 5 is chosen for the logarithm of the distances.]{\includegraphics[width=0.45\textwidth]{UKBB-Maha-outlier.png}}
	\caption{Homogeneous sample detection in the UK Biobank (UKBB), using robust Mahalanobis distances computed on the first 20 Principal Component scores (PCs) of UKBB.).\label{fig:homogeneous}}
\end{figure}
